Formalizing Stack Safety as a Security Property

### 2023-01-17 submission5/core.tex
Tweak to layout.

The paper is structured as follows. In \cref{sec:example}, we will walk through a function
call in a simple example machine and discuss how each of our properties applies to it,
informally. Then in \cref{sec:machine} we will introduce the formal machine model and give
its {\em security semantics}, described below. In \cref{sec:props} we give abbreviated
formal statements of the properties, while the full formalism is found in \cref{app:props}.
\Cref{sec:ext} gives the security semantics for the full, tested machine, and
\cref{sec:testing} describes the testing framework used to test it.
\Cref{sec:relwork,sec:future} discuss related and future work.
The remainder of this section introduces ideas that will be important throughout.

>>>>

The paper is structured as follows. In \cref{sec:example}, we will walk through a function
call in a simple example machine and discuss how each of our properties applies to it,
informally. Then in \cref{sec:props} we will introduce the machine model that we test, and give
its {\em security semantics}, described in brief below.
%In \cref{sec:props} we give abbreviated
%formal statements of the properties, while
The full formalism is found in \cref{app:props}.
\Cref{sec:testing} describes the testing framework used to test it.
\Cref{sec:relwork,sec:future} discuss related and future work.
The remainder of this section introduces ideas that will be important throughout.
